A Study of Common Bug Fix Patterns in Rust

### 2022-11-27 discussion.tex
ttv fixed

In our work there are three main threats to internal validity: (1) We use a weighting scheme which is based on a heuristic to give more values to tree elements closer to the leaves. In addition to that, we also manually adjusted the weights based on our knowledge of Rust. As this approach is based on our own judgement, it does not guarantee achieving optimal clusters. Nevertheless, our weighting scheme can be readjusted to find different patterns, which is why we made our pipeline publicly available. (2) The collected commits are the ones that fix a bug in a previously pushed commit. We do not consider the bugs that occur during a commit and also fixed during the same commit. (3) Our code embedding approach is based on the frequency of observed program elements in ASTs, and we use DBSCAN as our clustering algorithm. Other program code embedding methods and clustering algorithms (e.g. SLINK) might output new clusters that our pipeline is unable to find.

Threats to external validity can be described as: (1) The developers reporting the commits as bug fixing commits while they are not really fixing a functionality. Similarly, a commit message might not contain our target keywords while the commit is associated with bug fixing changes. (2) The selected projects might cause selection bias and therefore we might not have presented patterns that may exist in other projects.

>>>>

In our work there are two main threats to internal validity: (1) A threat to internal validity is confounding, where changes to what shows up in the embedding are not due to changes in the code being embedded. In this case, the weighting scheme may contribute to confounding because we manually adjusted the weights. Nevertheless, our weighting scheme can be readjusted to find different patterns, which is why we made our pipeline publicly available. (2) Our code embedding approach is based on the frequency of observed program elements in ASTs, and we use DBSCAN as our clustering algorithm. Other code embedding methods and clustering algorithms (e.g. SLINK) might output new clusters that our pipeline is unable to find. A threat to external validity is selection bias, where the benchmarks differ systematically from the actual world. The selected projects might cause selection bias and therefore we might not have presented patterns that may exist in other projects. Another threat to external validity can be the developers reporting the commits as bug fixing commits while they are not really fixing a functionality. Similarly, a commit message might not contain our target keywords while the commit is associated with bug fixing changes.
